---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rwetasks

<!-- badges: start -->
<!-- badges: end -->

rwetasks has simple functions for performing common tasks, such as calculating the number (and proportion) of people in each age group. It was built with beginning R users in mind. Experienced R users can already do everything covered here but with rwetasks they can do it easily and focus on the fun stuff!

Status: Currently in development aka not ready for prime time

## Installation

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("battenr/rwetasks")
```
## Using rwetasks

### count_percent

count_percent provides a way to quickly calculate the number (n) and proportion of each value of a variable, arranged by proportion. 

```{r count_percent example}
library(tidyverse)
library(rwetasks)

rwetasks::count_percent(mtcars, gear)
```

### count_percent_demo

count_percent_demo provides a way to quickly calculate the number (n) and proportion of each value of a variable, when you have multiple measures per participants (i.e., if you have longitudinal data, but want to calculate proportion of females for participants). 

```{r count_percent_demo example}
library(tidyverse)
library(rwetasks)

rwetasks::count_percent_demo(iris, Species, Petal.Width)
```


